---
title: "Prob HW1"
author: "Yingxi Ji"
date: "9/14/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# Problem 1 
## Part a
```{r}
## Creat a dataframe
ds = tibble(
  norm_samp = rnorm(8),
  norm_samp_pos = norm_samp > 0,
  norm_char = as.character("a","a","a","a","a","a","a","a"),
  samp_level = factor(c("low", "high", "medium", "high", "low", "medium", "high","low"), levels = c("low", "medium", "high")),
)
## Check levels
levels(pull(ds,samp_level ))

## Take the mean of each variable in the dataframe ds
mean_samp = mean(pull(ds, norm_samp))
mean_samp2 = mean(pull(ds, norm_samp_pos))

## Comment out vectors that can not be calculated

# mean_samp3 = mean(pull(ds, norm_char)), not logical, returning NA
# mean_samp4 = mean(pull(ds, samp_level)), not logical, returning NA
```

```{r, eval=FALSE}
##Apply `as.numeric()` function on vectors
as.numeric(pull(ds, norm_samp_pos))
as.numeric(pull(ds, norm_char))
as.numeric(pull(ds, samp_level))
```

NA means that it doesn't have a numeric meaning so it is not logical to use `as.numeric()`

## Part b
```{r}
samp_num = as.numeric(pull(ds,norm_samp_pos)) * pull(ds,norm_samp)
# samp_fac = as.factor(pull(ds,norm_samp_pos)) * pull(ds,norm_samp)
samp_final = as.numeric(as.factor(pull(ds,norm_samp_pos)))*pull(ds,norm_samp) 

## Call the values
samp_num
samp_final
```

When I have numeric values, they are treated as numbers so that I can do multiplication. For logic vector,it has values of either 0 or 1(meaning True and False). However, for character vector and factor vector, they are not math values so I can not take the mean and do multiplication. The last line is to convert the logical vector to factor vector then convert to numerical vector so I can still take the mean. Factor have different values after applying `as.numeric` function because the values of factor vector can be considered as levels.

## Problem 2
```{r}
set.seed(150)
## Create a dataframe
ds2 = tibble(
  x = rnorm(500),
  y = rnorm(500),
  samp_logical = x + y > 1,
  samp_numlog = as.numeric(samp_logical),
  samp_faclog = as.factor(samp_logical)
)

```
The size of the data set is (`r nrow(ds2)`, `r ncol(ds2)`) which means there are `r nrow(ds2)` rows and `r ncol(ds2)` columns. 

The mean is `r mean(pull(ds2, x))`.

The median is `r median(pull(ds2, x))`

The standard deviation is `r sd(pull(ds2, x))`

The proportion is `r length(which(pull(ds2,samp_logical)))/length(pull(ds2,samp_logical))`

```{r}
## Creat ggplots of Y~X, colored by different third variables
## logical
ggplot(ds2, aes(x = x, y = y, color = samp_logical))+geom_point() 
ggsave("polt_colored_by_logical_vector.pdf")

## numerical
ggplot(ds2, aes(x = x, y = y, color = samp_numlog))+geom_point() 
#ggsave("polt_colored_by_numeric_vector.pdf")

## factor
ggplot(ds2, aes(x = x, y = y, color =  samp_faclog))+geom_point() 
#ggsave("polt_colored_by_factor_vector.pdf")
```

The plot 1 is colored by logical vector. The red points are points with x + y < 1 and the blue points are poits with x + y > 1. There is an abovious sperate line between green and red data points. The line approximately follows y = - x. Points are symmetrically based on the line.


The plot 2 is colored by numeric vector. The colors are the intensity given by the numbers. There is an abovious sperate line between lighter and darker blue data points. The line approximately follows y = - x. Points are symmetrically based on the line

The plot 3 is colored by factor vector. The red points are points with x + y < 1 and the blue points are poits with x + y > 1. There is an abovious sperate line between green and red data points. The line approximately follows y = - x. Points are symmetrically based on the line






